---
title: "Power Analysis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)

library(tidyverse)
library(brms)
library(broom)
library(ggthemes)
library(lme4)
library(tidyboot)
library(ggpubr)
library(tidybayes)
library(coda)

hdi_upper<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","upper"])
}

hdi_lower<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","lower"])
}
```

# Load data

Each test session produced a separate `.csv` file. Here we read in all files and combine them in one datafile. 
```{r}
# read_plus <- function(flnm) {
#     read_csv(flnm, skip = 3) %>% 
#         mutate(filename = flnm, 
#                trial = 1:length(SampleSound),
#                RT = as.character(RT))
# }
# 
# 
# raw_data <- list.files(path = "../Data/Testing/",
#                        pattern = "*.csv",
#                        full.names = T) %>% 
#   map_df(~read_plus(.))
# 
# data <- raw_data %>%
#   filter(trial != 1)%>%
#   mutate(correct = ifelse(Correct_1 == "YES" | Correct_1 == "YES (R)", 1, 0), # re-code response variable for analysis. "Yes (R)" refers to trials with a reward
#          shape_combination  = paste(Correct,Foil1, sep = "_"), # generate variable for specific shape combination
#          session = as.numeric(factor(filename)), # generate numeric session number,
#          cont_trial = trial + (session -1) * 100, #generate a continuous trial number across sessions
#          condition = ifelse(grepl("Slide", Correct) | grepl("shape", Correct),"test", "filler"), # generate variable tracking whether it's a test or a filler trial. Test trials had pictures that were named E/RSlide or E/Rshape
#          RT = as.numeric(RT),
#          test_shape = ifelse(grepl("ESlide", Correct) | grepl("Eshape", Correct),"edgy", "round"),
#          test_shape = ifelse(condition == "test", test_shape, "NA"))%>%
#   na.omit(correct)%>%
#   select(session, trial,cont_trial, condition, SampleSound, test_shape, shape_combination,correct, RT)
# 
# write_csv(data, "../Data/data.csv")

data <- read_csv("../Data/data.csv")
```
# Descriptives

## Number of Trials

Number of trials per condition. There were 30 sessions in total, each with 10 test trials. There are 2 filler trials missing, because they timed out (> 6000ms to react). 

```{r}
data %>%
  group_by(condition)%>%
  summarise(n())
```

## Reaction times

Visualize reaction time by correct choice and trial time to check if responses were slower / faster in test trials compared to filler trials. Responses seem to be slightly faster in test trials, but still fall very well inside the distribution of filler trials. 

```{r}
rt_data <- data%>%
  mutate(correct = ifelse(correct == 1, "correct", "incorrect"))

rt_plot <- ggplot(rt_data, aes(x = RT, col = condition, fill = condition, lty = correct))+
  geom_density(alpha = .3)+
  xlim(0,6000)+
  xlab("Reaction Time")+
  ylab("")+
  scale_color_colorblind(name = "Condition")+
  scale_fill_colorblind(name = "Condition")+
  scale_linetype_discrete(name = "Choice")+
  theme_minimal()+
  theme(axis.text.y = element_blank(),
        axis.ticks.y  = element_blank(),
        legend.position = c(0.7,0.6),
        legend.direction = "vertical",
        legend.box = "horizontal")
```

# Results

## Statistical analysis

```{r}
test_data <- data %>%
  filter(condition == "test")%>%
  mutate(z_trial = scale(cont_trial))

filler_data <- data %>%
  filter(condition == "filler")%>%
  mutate(z_trial = scale(cont_trial))

```

### Test trials 

#### Comparison to chance

We use a generalized linear mixed model to analyze performance. In such a model, an intercept of 0 in link space corresponds to a proportion of correct choices of 0.5. Thus, we infer that if the 95% credible interval around the intercept estimate does not include 0, performance is reliably above chance.

All models use default priors as implemented in the `brms` package.

```{r}
# model takes a minute or two to initialize and run.
# load rds file if you don't want to wait or if you want to reproduce the numbers in the exact manuscript

bm_test <- brm(correct ~ 1 + (z_trial | SampleSound ), # + (z_trial | shape_combination),
          data = test_data,
          family = bernoulli(),
          cores = 4,
          chains = 4,
          iter = 5000,
          control = list(adapt_delta = 0.95))

#saveRDS(bm_test, "saves/model_test.rds")

bm_test <-readRDS("saves/model_test.rds")

bm_test
```

```{r}
bm_test%>%
  spread_draws(b_Intercept)%>%
  ggplot(aes(x = b_Intercept, fill = stat(x < -0.15 | x > 0.55))) +
  stat_halfeye(alpha = .7)+
  geom_vline(xintercept = 0, linetype = "dashed") +
  xlab("Intercept")+
  scale_fill_manual(values = c("gray80", "firebrick"), name = "95% Credible intervall", labels = c("< 2.5% | > 97.5%","2.5% - 97.5%"))+
  guides(fill = F)+
  theme_minimal()
```


#### Shape preference

```{r}
# load .rds file if you don't want to run the model

bm_shape <- brm(correct ~ test_shape + (z_trial | SampleSound ), #+ (z_trial | shape_combination),
          data = test_data,
          family = bernoulli(),
          cores = 4,
          chains = 4,
          iter = 5000,
          control = list(adapt_delta = 0.95))

#saveRDS(bm_shape, "saves/model_shape.rds")

bm_shape <-readRDS("saves/model_shape.rds")

bm_shape
```

```{r}
bm_shape%>%
  spread_draws(b_test_shaperound)%>%
  ggplot(aes(x = b_test_shaperound, fill = stat(x < -0.48 | x > 1.00))) +
  stat_halfeye(alpha = .7)+
  geom_vline(xintercept = 0, linetype = "dashed") +
  xlab("Estimate: test shape")+
  scale_fill_manual(values = c("gray80", "firebrick"), name = "95% Credible intervall", labels = c("< 2.5% | > 97.5%","2.5% - 97.5%"))+
  guides(fill = F)+
  theme_minimal()
```

### Filler trials

#### Comparison to chance

```{r}
# model takes f long time to run

bm_filler <- brm(correct ~ 1 + (z_trial | SampleSound ),# + (z_trial | shape_combination),
          data = filler_data,
          family = bernoulli(),
          cores = 4,
          chains = 4,
          iter = 5000,
          control = list(adapt_delta = 0.99, max_treedepth = 20))

#saveRDS(bm_filler, "saves/filler_model.rds")

bm_filler <- readRDS("saves/filler_model.rds")

bm_filler

```


```{r}
filler_samples <- bm_filler%>%
  spread_draws(b_Intercept)%>%
  ggplot(aes(x = b_Intercept, fill = stat(x < 1.69 | x > 2.31))) +
  stat_halfeye(alpha = .7)+
  geom_vline(xintercept = 0, linetype = "dashed") +
  xlab("Intercept")+
  scale_fill_manual(values = c("gray80", "firebrick"), name = "95% Credible intervall", labels = c("< 2.5% | > 97.5%","2.5% - 97.5%"))+
  guides(fill = F)+
  theme_minimal()
```


# Visualizations

## Correct choice in filler and test trials

Visualize the results overall (A) and by session (B). Error bars show 95% confidence intervals. Light dots in A show session means.

```{r}
# data from individual sessions
plot_session <- data%>%
  group_by(session,condition)%>%
  tidyboot_mean(col = correct)

# model estimates
model_est <- bind_rows(
  fixef(bm_test)%>%as_tibble()%>%mutate(condition = "test"),
  fixef(bm_filler)%>%as_tibble()%>%mutate(condition = "filler"),
)%>%
  mutate(mean = plogis(Estimate),
         uci = plogis(Q2.5),
         lci = plogis(Q97.5))
  

res_plot <- ggplot()+
  geom_hline(yintercept = 0.5, lty = 2)+
  geom_jitter(data = plot_session, aes(x= condition, y = mean, col = condition), alpha = 0.2, width = 0.1, height = 0)+
  geom_pointrange(data = model_est, aes(x = condition, y = mean, ymax = uci, ymin = lci, col = condition),pch = 5)+
  ylim(0,1)+
  ylab("Proportion correct")+
  xlab("Condition")+
  scale_color_colorblind(name = "Condition")+
  guides(col = F)+
  theme_minimal()

sess_plot <- ggplot(plot_session, aes(x = session, col = condition))+
  geom_hline(yintercept = 0.5, lty = 2)+
  geom_point(aes(y = mean))+
  #geom_pointrange(aes(y = mean, ymax = ci_upper, ymin = ci_lower), pch = 5)+
  geom_line(aes(y= mean, col = condition))+
  ylim(0,1)+
  #facet_grid(condition~.)+
  ylab("Prop. correct")+
  xlab("Session")+
  scale_color_colorblind(name = "Condition")+
  theme_minimal()+
  theme(legend.position = c(0.5,0.1),
        legend.direction = "horizontal")


```
## Correct choice in edgy vs. round trials

In test trials, Kanzi either had to match a round sound to a round shape or a edgy sound to a edgy shape to be correct. The plot below shows correct responses for round vs. edgy test trials. Error bars show 95% confidence intervals, light dots show session means. 

```{r}
plot1 <- data%>%
  filter(condition == "test")%>%
  mutate(shape = ifelse(grepl("ESlide", Correct) | grepl("Eshape", Correct),"edgy", "round"))%>%
  group_by(session, shape)%>%
  summarise(mean = mean(correct))

shape_est <- bm_shape%>%
  spread_draws(b_Intercept,b_test_shaperound)%>%
  mutate(edgy = b_Intercept,
         round = b_Intercept + b_test_shaperound)%>%
  select(round, edgy)%>%
  gather(shape, value)%>%
  group_by(shape)%>%
  summarise(mean = mean(value),
            uci = hdi_upper(value),
            lci = hdi_lower(value))%>%
  mutate_if(is.numeric, plogis)


shape_plot <- ggplot()+
  geom_hline(yintercept = 0.5, lty = 2)+
  geom_jitter(data = plot1, aes(x= shape, y = mean, col = shape), alpha = 0.2, width = 0.1, height = 0)+
  geom_pointrange(data = shape_est, aes(x = shape, y = mean, ymax = uci, ymin = lci, col = shape), pch = 5)+
  #geom_line(aes(y= mean, col = shape))+
  ylim(0,1)+
  ylab("Prop. correct")+
  xlab("Shape")+
  scale_color_ptol()+
  guides(col = F)+
  theme_minimal()
```

## Combined plot

```{r}
ggarrange(
  
  res_plot,
  
  ggarrange(
    rt_plot,
    
    ggarrange(
    sess_plot,
    shape_plot,
    nrow = 1,
    ncol = 2,
    widths = c(1.5,1),
    labels = c("C","D")
    ),
    nrow = 2,
    ncol = 1,
    labels = c("B","")),
  nrow = 1,
  ncol = 2,
  labels = c("A",""),
  widths = c(1,1.3)
)

ggsave("figures/results.png", height = 3, width = 7, scale = 1.4)
```



